---
title: "HHmicrobiome_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HHmicrobiome_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Start by loading the package!
```{r setup}
library(HHmicrobiome)
```
Clean your data sets! Using the "testing1" and "testing2" example datasets, input your datasets into the HHclean function along with the year that the microbial data was collected.

Assign the cleaned data sets to new variable names.
```{r}
HHclean(testing1, 2016)

clean2016 <- HHclean(testing1, 2016)

HHclean(testing2, 2017)

clean2017 <- HHclean(testing2, 2017)
```
Plot your data set! If you would like to see a stacked bar chart output of the microbial data from one year, input one of your cleaned and renamed datasets into the HHplot function.
```{r}
HHplot(clean2016)
```

If you would like to compare the microbial data collected from the same plots during different years, input two of your cleaned and renamed datasets into the HHplot function.

```{r}
HHplot(clean2016, clean2017)
```


